Relative parabolic factorizations of Chevalley groups

### 2015-09-01 paper.tex
Proved lemma 3

For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
\begin{equation}\label{rel:R3}
w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta,\alpha \rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
\end{equation}
where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
\begin{lemma}
\begin{thmlist}
\item For every roots $\alpha, \beta \in \Phi$ having the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
\item The elementary group $\E(\Phi, R)$ (resp. $\EP_r(R)$, $1\leq r\leq \ell$) is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in S$,
       where $S = \Pi \cup -\Pi$ (resp. $S = \Pi \cup -\Pi \setminus \{ -\alpha_r \}$).
\item Assume that for a simple root $\alpha_s\in \Pi$ one has $m_s(\alpha_\mathrm{max}) = 1$.
       Then for $\alpha, \beta \in \Sigma^\pm_s$ having the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
\end{thmlist}
\end{lemma}
\begin{proof}
 The first statement of the lemma follows from identity~\ref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.

 The prove the second statement observe that the subgroup $\langle X_\alpha(R) \mid \alpha \in S \rangle$ contains $\widetilde{W}(\Phi)$ (resp. $\widetilde{W}(\Delta_s)$).
 %TODO: FINISH PROOF
\end{proof}

@@

>>>>

For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
\begin{equation}\label{rel:R3}
w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta,\alpha \rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
\end{equation}
where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
\begin{lemma} \label{lemma:weylfacts} Let $\Phi$ be an irreducible root system and let $I$ be an ideal of $R$. Assume also that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$.
\begin{thmlist}
\item \label{item-trans1} For every roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
\item \label{item-trans2} For $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
\item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
\end{thmlist}
\end{lemma}
\begin{proof}
The first statement of the lemma follows from identity~\ref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.

The same argument combined with~\cref{lemma:abs} also proves the second statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.

To prove the third assertion notice that the subgroup $\langle X_\alpha(R) \mid \alpha \in \Pi \cup -\Pi \rangle$ contains $\widetilde{W}(\Phi)$ and therefore contains all other root subgroups $X_\alpha(R)$, $\alpha\in \Phi$. \end{proof}

@@

\begin{rem}
Notice that by the same token as in the proof of~\cref{lemma:weylfacts} one can show that $\EP_s(R)$ is generated as an abstract group by root subgroups $X_\alpha(R)$, $\alpha\in \Pi \cup (-\Pi\setminus \{ -\alpha_ s\})$, $1\leq s\leq \ell$.
\end{rem}
